Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-11-10 papers/integration/omm_integ.tex
Adds section labels, and completes the section on weight maps in results

\section{Introduction}

@@

\section{Material \& Methods}

@@

\subsubsection{Co-ordinates in the world}

@@

\subsection{Model development framework}

@@

\subsection{Existing brain model}

@@

\subsubsection{Population activity and retinotopic mapping}

@@

% Section - description of new brainstem model
\subsection{Brainstem model}

@@

% Section - description of biomechanical model
\subsection{biomechanical eye}

@@

% Section - description of the integration. scientific and
% technical. Already
\subsection{Integrating the models and closing the loop}

@@

\section{Results}

\subsection{Weight maps}

We found the best parameters for the exponential in
Eq.~\ref{eq:weightmaps} ($i$ and $j$) by a manual tuning
process. After selecting values for $i$ and $j$ in either the
horizontal or vertical/oblique channels, we ran the model 6 times at
each of 8 target eccentricities (7\dg--14\dg) which were purely in the
direction of the newly parameterised channel. The training saccades
were produced as described below in Sect.~\ref{sec:singlesaccades},
with the same fixation and target luminances (crosses of magnitude 0.2
and 0.3) but with the fixation offset and target onset occurring at
0.2~s. We measured the end-point of the saccade by detecting the
location at which the saccade velocity had dropped below 0.005 of its
peak. We iterated until the mean saccade endpoint plotted versus
target was close to the ideal straight line---see
Fig.~\ref{sacc_vs_targ}(a) \& \rvw{(b)}. We applied the same parameters to
both directions of each channel; $i_{up} = i_{down} = 0.00195$,
$j_{up} = j_{down} = 0.075$, $i_{left} = i_{right} = 0.0016$ and
$j_{left} = j_{right} = 0.067$. The resulting weight maps (where the
oblique maps are 1/10$^{\mathrm{th}}$ of the vertical maps, as
described earlier) are shown in Fig.~\ref{weightmaps}.

\rvw{Fig.~\ref{weightmaps}(a) shows the weight map for the muscle
which rotates the eye to the left. As we modelled a left eye, this
actuates the lateral rectus muscle. The exponential rise is seen in
the $r$ direction; as $r$ increases, so the connection strength to the
SBG channel rises exponentially. The connection strength is greatest
along the centre line, for a value of $\phi$ which corresponds to a
purely leftward movement. Note that $\phi$ is presented in neural
coordinates, and not in degrees or radians. $\phi=$37.5 corresponds
to movements left. In regions of the map for which there is no
leftward movement, that is, in the half of the map which corresponds
to any movement with a rightward component, the `left' weight map is
0. Fig.~\ref{weightmaps}(d) shows the weight map for rightward
movements, actuating the medial rectus muscle of the eye. The map is a
mirror of Fig.~\ref{weightmaps}(a), reflected about the line
$phi$=25. ETC ETC for DOWN UP and Z+, Z-.}
% From map_modelling2.m:
%    yh=0.0016*exp(0.067.*x);
%    yv=0.00195*exp(0.075.*x);

\subsection{Saccade accuracy}

@@

To bring our model in line with these results, whilst maintaining the
eccentricity dependent activity in basal ganglia, we hypothesised that
a `widening projection' exists between two maps in superior
colliculus. \rvw{As described in the Methods section, there is
now experimental evidence for similar projections
\citep{ghitani_excitatory_2014,bayguinov_hard-wired_2015} making this
a plausible suggestion.}  Activities in one SC\_deep layer remains
eccentricity-dependent, with loops back to thalamus and cortex and
through basal ganglia.  This activity is then fed through a
projection, which applies a Gaussian projection field, whose width
increases with increasing stimulus eccentricity according to
Eq.~\ref{eq:widening}.  The activity in this second SC\_deep layer is
then fed to the weight maps of the SBG. This model was called
`TModel4'. TModel4 was parameterised such that its horizontal and
vertical error was similar---so that its equivalent of
Fig.~\ref{sacc_vs_targ} showed a similar sum of squares error.

@@

\subsection{Single saccades} \label{sec:singlesaccades}

@@

\subsection{Saccade Latencies}

@@

\subsection{Saccade sequences}

@@

\section{Discussion}

>>>>

\section{Introduction} \label{sec:introduction}

@@

\section{Material \& Methods} \label{sec:methods}

@@

\subsubsection{Co-ordinates in the world} \label{sec:methods:coords}

@@

\subsection{Model development framework} \label{sec:methods:framework}

@@

\subsection{Existing brain model} \label{sec:methods:existing}

@@

\subsubsection{Population activity and retinotopic mapping}
\label{sec:mapping}

@@

% Section - description of new brainstem model
\subsection{Brainstem model} \label{sec:methods:brainstem}

@@

% Section - description of biomechanical model
\subsection{biomechanical eye} \label{sec:methods:eye}

@@

% Section - description of the integration. scientific and
% technical. Already
\subsection{Integrating the models and closing the loop}
\label{sec:methods:integrating}

@@

\section{Results} \label{sec:results}

\subsection{Weight maps} \label{sec:results:weightmaps}

We found the best parameters for the exponential in
Eq.~\ref{eq:weightmaps} ($i$ and $j$) by a manual tuning
process. After selecting values for $i$ and $j$ in either the
horizontal or vertical/oblique channels, we ran the model 6 times at
each of 8 target eccentricities (7\dg--14\dg) which were purely in the
direction of the newly parameterised channel. The training saccades
were produced as described below in Sect.~\ref{sec:results:singlesaccades},
with the same fixation and target luminances (crosses of magnitude 0.2
and 0.3) but with the fixation offset and target onset occurring at
0.2~s. We measured the end-point of the saccade by detecting the
location at which the saccade velocity had dropped below 0.005 of its
peak. We iterated until the mean saccade endpoint plotted versus
target was close to the ideal straight line---see
Fig.~\ref{sacc_vs_targ}(a) \& \rvw{(b)}. We applied the same parameters to
both directions of each channel; $i_{up} = i_{down} = 0.00195$,
$j_{up} = j_{down} = 0.075$, $i_{left} = i_{right} = 0.0016$ and
$j_{left} = j_{right} = 0.067$.

The resulting weight maps (where the oblique maps are
1/10$^{\mathrm{th}}$ of the vertical maps, as described earlier) are
shown in Fig.~\ref{weightmaps}.
%
\rvw{First, recall that the $r$ axis of the neural surface corresponds
to the amplitude of a saccade and the $\phi$ axis indicates the polar
direction of the saccade, as described in Sect.~\ref{sec:mapping} and
Fig.~\ref{fig:mapping}. Fig.~\ref{weightmaps}(a) shows the weight map
for the muscle which rotates the eye to the left. As we modelled a
left eye, this actuates the lateral rectus muscle. The exponential
rise of Eq.~\ref{eq:weightmaps} is seen in the $r$ direction; as $r$
increases, so the connection strength to the SBG channel rises
exponentially. The connection strength is greatest along the centre
line, for a value of $\phi$ which corresponds to a purely leftward
movement. Note that $\phi$ is presented in neural coordinates, and not
in degrees or radians; 1$\leq\phi\leq$50 corresponds to a range of
0\dg~to 360\dg; $\phi=$38.5 corresponds to movements left. The
connections strength drops away sinusoidally as $\phi$ moves away from
the centre line at $\phi=$38.5. In regions of the map for which there
is no leftward movement, that is, in the half of the map which
corresponds to any movement with a rightward component, the `left'
weight map is 0. Fig.~\ref{weightmaps}(d) shows the weight map for
rightward movements, actuating the medial rectus muscle of the
eye. The line of maximum connection strength is along $\phi=$13.5. The
map is a mirror of Fig.~\ref{weightmaps}(a), reflected about the line
$\phi$=26. The `left' and `right' weight maps are orthogonal; the
non-zero region of the `left' map is zero in the `right' map and vice
versa. Fig~\ref{weightmaps}(b) \& (d) show the weight maps for
downward and upward eye movements; the `down' map activates the SBG
channel for the inferior rectus muscle, the `up' map activates the
superior rectus. Note that `down' is not orthogonal either to `left'
or `right' because a saccade down and left is achieved by
simultaneously activating both the lateral and inferior rectus
muscles. However, the `up' map \e{is} orthogonal to the `down' map and
spans the edges of the surface where $\phi$ rolls over from 1 to
50. The line of maximum connection strength for the `up' map is along
$\phi=$1; for `down' $\phi=$26. Based on the training described in
Sect.~\ref{sec:methods:integrating}, the maps driving the superior
oblique (`Z+') and inferior oblique (`Z-') muscles were set to
1/10$^{\mathrm{th}}$ of the `down' and `up' maps.}
% From map_modelling2.m:
%    yh=0.0016*exp(0.067.*x);
%    yv=0.00195*exp(0.075.*x);

\subsection{Saccade accuracy} \label{sec:results:accuracy}

@@

To bring our model in line with these results, whilst maintaining the
eccentricity dependent activity in basal ganglia, we hypothesised that
a `widening projection' exists between two maps in superior
colliculus. \rvw{As described in
Sect.~\ref{sec:methods:integrating}, there is
now experimental evidence for similar projections
\citep{ghitani_excitatory_2014,bayguinov_hard-wired_2015} making this
a plausible suggestion.}  Activities in one SC\_deep layer remains
eccentricity-dependent, with loops back to thalamus and cortex and
through basal ganglia.  This activity is then fed through a
projection, which applies a Gaussian projection field, whose width
increases with increasing stimulus eccentricity according to
Eq.~\ref{eq:widening}.  The activity in this second SC\_deep layer is
then fed to the weight maps of the SBG. This model was called
`TModel4'. TModel4 was parameterised such that its horizontal and
vertical error was similar---so that its equivalent of
Fig.~\ref{sacc_vs_targ} showed a similar sum of squares error.

@@

\subsection{Single saccades} \label{sec:results:singlesaccades}

@@

\subsection{Saccade Latencies} \label{sec:results:latencies}

@@

\subsection{Saccade sequences} \label{sec:results:sequences}

@@

\section{Discussion} \label{sec:discussion}
